\documentclass[11pt,letterpaper]{hmcpset}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{enumerate}

\name{ }
\class{MATH 60, Sec. }
\assignment{HW 2}
\duedate{9 September 2016}

\newcommand{\bvec}[1]{$\vec{\textbf{#1}}$}

\begin{document}
	\problemlist{Colley Chapter 2.3.\{33, 38, 42\}, 2.4.\{16, 22, 29a\}}
	
	\begin{problem}[2.3.33] Find the matrix $D\mathbf{f}(\mathbf{a})$ of partial derivatives where $\mathbf{f}$ and $\mathbf{a}$ are as indicated:
	$$ \mathbf{f}(s,t) = (s^2, st, t^2), \medskip \mathbf{a} = (-1,1)$$
	\end{problem}
	
	\begin{solution}
		\vfill
	\end{solution}
	
	\newpage
	
	\begin{problem}[2.3.38] Find an equation for the plane tangent to the graph of $z = 4\cos{xy}$ at the point $(\pi/3,1,2)$.
	\end{problem}
	
	\begin{solution}
		\vfill
	\end{solution}
	
	\newpage
	
	\begin{problem}[2.3.42] Suppose that you have the following information concerning a differentiable function $f$:
	$$ f(2,3) = 12, f(1.98, 3) = 12.1, f(2, 3.01) = 12.2$$
	\begin{enumerate}[(a)]
		\item Give an approximate equation for the plane tangent to the graph of $f$ at (2,3,12).
		\item Use the result of part (a) to estimate $f(1.98, 2.98)$.
	\end{enumerate}
	\end{problem}
	
	\begin{solution}
		\vfill
	\end{solution}
	
	\newpage
	
	\begin{problem}[2.4.16] Determine all second-order partial derivatives (including mixed partials).
	$$ f(x,y) = ln\left(\frac{x}{y}\right) $$
	\end{problem}
	
	\begin{solution}
		\vfill
	\end{solution}
	
	\newpage
	
	\begin{problem}[2.4.22] Consider the function $F(x,y,z) = 2x^3y + xz^2 + y^3z^5-7xyz$.
	\begin{enumerate}[(a)]
		\item Find $F_{xx}, F_{yy},$ and $F_{zz}$.
		\item Calculate the mixed second-order partials $F_{xy}, F_{yx}, F_{xz}, F_{zx}, F_{yz},$ and $F_{zy},$ and verify Theorem 4.3.
	\end{enumerate}
	\end{problem}
	
	\begin{solution}
		\vfill
	\end{solution}
	
	\newpage
	
	\begin{problem}[2.4.29a] The three-dimensional \textbf{heat equation} is the partial differential equation
	$$ k \left( \frac{\partial^2T}{\partial x^2} + \frac{\partial^2T}{\partial y^2} + \frac{\partial^2 T}{\partial z^2} \right) = \frac{\partial T}{\partial t} $$
	where $k$ is a positive constant. It models the temperature $T(x,y,z,t)$ at the point $(x,y,z)$ and time $t$ of a body in space.
	\begin{enumerate}[(a)]
		\item We examine a simplified version of the heat equation. Consider a straight wire "coordinatized" by $x$. Then the temperature $T(x,t)$ at time $t$ and position $x$ along the wire is modeled by the one-dimensional heat equation
		$$ k  \frac{\partial^2T}{\partial x^2} = \frac{\partial T}{\partial t}. $$
		Show that the function $T(x,t) = e^{-kt}\cos{x}$ satisfies this equation. Note that if $t$ is held constant at value $t_0$, then $T(x,t_0)$ shows how the temperature varies along the wire at time $t_0$. Graph the curves $z = T(x, t_0)$ for $t_0 = 0,1,10,$ and use them to understand the graph of the surface $z=T(x,t)$ for $t \geq 0$. Explain what happens to the temperature of the wire after a long period of time.
	\end{enumerate}
	\end{problem}
	
	\begin{solution}
		\vfill
	\end{solution}
	
\end{document}